Data Specialization for a Staged Lambda Calculus

### 2014-11-06 paper/splitting.tex
Setting up why the definition of Stage 1 splitting is what it is.

Splitting a stage \bbone\ term $\colone e A$ produces a term and a function,
which respectively contain all the stage \bbone\ and stage \bbtwo\
subcomputations of $e$. The situation is more complex than when splitting stage
\bbtwo\ terms; to see why, consider the correctness criterion for splitting
stage \bbone\ terms.

Stage \bbone\ evaluation of $e$, via $e\mathbin{\redonesym}[\xi;v]$,
yields a table of (stage \bbtwo) residuals $\xi$, and a (stage \bbone) partial
value $v$. It is tempting to compare the two results of evaluating $e$ to the
two results of splitting it. To see where this goes wrong, consider the stage
\bbone\ term
\begin{lstlisting}
1`(1+2, next{`2`hold{`1`3+4`2`} + 5`1`})`
\end{lstlisting}
which evaluates to
\begin{lstlisting}
2`[yhat|->7+5]` 1`(3,next{`2`yhat`1`})`
\end{lstlisting}
This partial value contains a $\next$, and so is itself multistaged:
intuitively, its stage \bbone\ part is \texttt{3}, while its stage \bbtwo\ part
is $\mathtt{\hat{y}}$, which is bound to \texttt{7+5}.

\ur{So what goes wrong?  I have no idea what you are talking about at
  this point.  The thought seems unfinished.}

>>>>

The goal of stage 2 splitting was to generate a precomputation and resumer such that the resumer and the \lang\ residual reduce to the same final value. However, stage~\bbone\ terms do not reduce to final values, rather they reduce to residual tables and partial values.  For example, consider the stage 1 term: 
\begin{lstlisting}
1`(1+2, next{`2`hold{`1`3+4`2`} + 5`1`})`
\end{lstlisting}
which evaluates (via $\mathbin{\redonesym}$), to the following residual table and a multi-stage tuple:

\begin{lstlisting}
2`[yhat|->7+5]` 1`(3,next{`2`yhat`1`})`
\end{lstlisting}

%Like stage \bbtwo\ splitting, splitting a stage~\bbone\ term $\colone e A$ produces a term $c$ containing all stage~\bbone\ subcomputations in $e$ and a resumer function %$l.r$ containing all stage~\bbtwo\ subcomputations.  
%which respectively contain all the stage \bbone\ and stage \bbtwo\
%subcomputations of $e$. 
%But where the stage \bbtwo\ splitting goal was phrased terms ensure.

%The situation is more complex than when splitting stage
%\bbtwo\ terms; to see why, consider the correctness criterion for splitting
%stage \bbone\ terms.

%Stage \bbone\ evaluation of $e$, via $e\mathbin{\redonesym}[\xi;v]$,
%yields a table of (stage \bbtwo) residuals $\xi$, and a (stage \bbone) partial
%value $v$.

Intuitively for splitting TO MATCH THIS THING ABOVE.  It needs to match the 3, and the resumer should reduce to the same value as the reified partial value.

%It is tempting to compare the two results of evaluating $e$ to the
%two results of splitting it.

%To see where this goes wrong, consider the stage
%\bbone\ term
%\begin{lstlisting}
%1`(1+2, next{`2`hold{`1`3+4`2`} + 5`1`})`
%\end{lstlisting}
%which evaluates to
%\begin{lstlisting}
%2`[yhat|->7+5]` 1`(3,next{`2`yhat`1`})`
%\end{lstlisting}
%This partial value contains a $\next$, and so is itself multistaged:
%intuitively, its stage \bbone\ part is \texttt{3}, while its stage \bbtwo\ part
%is $\mathtt{\hat{y}}$, which is bound to \texttt{7+5} in the table.
